### 2015-04-26 conclusion.tex
fix

In this paper, we present \whoop, a new fully automatic approach for (i) finding data races in device drivers and (ii) accelerating bug-finding using race-related information. In the heart of our approach, we combine static lockset analysis with sound sequentialization and automated theorem proving. Our lockset analysis enforces the locking discipline that two threads accessing the same shared resource must hold at least one common lock, and reports a potential data race if this discipline is violated.

>>>>

In this paper, we presented \whoop, a new fully automatic approach for (i) finding data races in device drivers and (ii) accelerating bug-finding using race-related information. In the heart of our approach, we combine static lockset analysis with sound sequentialization and automated theorem proving. Our lockset analysis enforces the locking discipline that two threads accessing the same shared resource must hold at least one common lock, and reports a potential data race if this discipline is violated.
